Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-21 paper/current/main.tex
edit on sk data

\begin{document} %{{{
\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\author[1,\Yinyang]{Dakota Murray}
\author[1,2,\Yinyang]{Jisung Yoon}
\author[1]{Sadamori Kojaku}
\author[3]{Rodrigo Costas}
\author[2,4,5]{Woo-Sung Jung}
\author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
\author[1,6,7]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}

@@

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD. in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.

>>>>

\begin{document} %{{{
\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\author[1,\Yinyang]{Dakota Murray}
\author[1,2,\Yinyang]{Jisung Yoon}
\author[1]{Sadamori Kojaku}
\author[3]{Rodrigo Costas}
\author[2,4]{Woo-Sung Jung}
\author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
\author[1,6,7]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}

@@

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD. in Korea, The data contain reservation trajectories of each customer spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.
